A unified pseudo-$C_\ell$ framework

### 2018-08-31 doc/Paper/main.tex
added timing plot

     \begin{figure}
     \centering
     \includegraphics[width=0.9\columnwidth]{time_scaling}
     \caption{Computing time for the auto-power spectra of curved-sky spin-0 (data 00, hollow circles), and spin-2 (data 22, solid triangles) contamination-free maps, as wells as their cross-power (data 02, solid circles) as a function of $\ell_{max}$. We include the expected scaling for the pseudo-$C_{\ell}$ estimator (solid line) and force it to go through the point for the spin-0 auto-power at $\ell=96$ showing remarkable agreement.}
     \label{fig:scaling_lmax}
     \end{figure}

@@

    In addition, we also check the parallel performance of \nmt. We proceed again, as in the previous case, to compute the auto- and cross-power spectra of spin-0 and spin-2 fields with no contaminants for maps with $N_{side}=256$ and $N_{side}=1024$ and we vary the number of \texttt{OpenMP} threads from 1 to 32 in powers of 2. The results can be seen in Figure~\ref{fig:scaling_nthreads}. We can see that the operations involving spin-0 fields seem to be more affected by the number of threads used, however, the spin-2 auto-power spectra computing time seems to be very stable for any number of threads larger than 2. \todo{Discuss this further? Take the second part out? Ideas?}

    \begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{time_scaling_threads}
     \caption{Computing time for auto-power spectra of spin-0 (red lines) and spin-2 (cyan lines) contaminant-free maps, and their cross-power spectra (blue lines) as a function of the number of \texttt{OpenMP} threads used for the computation. We check maps with $N_{side}=256$ (solid lines) and $N_{side}=1024$ (broken lines).}
     \label{fig:scaling_nthreads}
     \end{figure}

>>>>

     \begin{figure}
     \centering
     \includegraphics[width=0.99\columnwidth]{time_scaling}
     \includegraphics[width=0.99\columnwidth]{timing}
     \caption{Computing time for the auto-power spectra of curved-sky spin-0 (data 00, hollow circles), and spin-2 (data 22, solid triangles) contamination-free maps, as wells as their cross-power (data 02, solid circles) as a function of $\ell_{max}$. We include the expected scaling for the pseudo-$C_{\ell}$ estimator (solid line) and force it to go through the point for the spin-0 auto-power at $\ell=96$ showing remarkable agreement.}
     \label{fig:scaling_lmax}
     \end{figure}

@@
